\documentclass[10pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{fontawesome}

\usepackage[compact]{titlesec}
\usepackage{ragged2e}

\usepackage{newcent}   % uses new century schoolbook postscript font  
\usepackage{enumitem}
\usepackage[none]{hyphenat}
\usepackage{multicol}
\usepackage{tabu}
\linespread{0.9}

\setlength{\textheight}{11in}

\titleformat{\section}
	{\normalfont\scshape}{\thesection}{}{}
\titlespacing{\section}{0pt}{4pt}{4pt}

\begin{document}
\centering
{\Large William Arnold}
\centering       

\begin{tabu}{X[l]X[c]X[r]}
(510)-529-8523 & willarnold@berkeley.edu & linkedin.com/in/{\textasciitilde}arnold
\end{tabu} 

\section*{EDUCATION}
		\begin{tabu}{X[l]X[r]}
			   University of California, Berkeley, Class of 2021 & Focuses \\
 			   Bachelor of Science in Electrical Engineering & Machine Learning \\ 
 			   and Computer Science & Computer Security  \\
		\end{tabu}

\justify
\section*{EXPERIENCE}
				Activate Inc., at Google. San Francisco, CA.
				\newline
	                  \hspace*{1em}\begin{tabu}{X[l]X[r]}
	                  	CTO and Technical Project Lead & February 2016 - Current
	                  \end{tabu}	                  		
	                   \begin{itemize} 
	                    		\item[] Organized and Implemented a feature-diverse unsupervised machine learning algorithm to identify the most attractive food concepts around 50+ locations in the Bay Area for a Fortune 500 company.
	                    		\item[] Collaborated with Economists from NYU in order to create a scalable, demographic and restaurant quality-based AI to predict restaurant success at 1000+ target points across California.
	                    		\item[] Independently created a deep learning-based AI to predict how individuals move in Google Cafes to reduce food waste and ensure more effective resource utilization in future Google buildings
	                    		\item[] Created a pathfinding-based algorithm to determine the relative size of food courts in retail-based malls and office buildings
	                    \end{itemize}
	                    		
	   		
			   	Skydeck Berkeley. Berkeley, CA.
			   	\newline
			 		\hspace*{1em}\begin{tabu}{X[l]X[r]}
	                  	 Software Engineer, Data and Financial Analyst & July 2016 - Current
	                 \end{tabu}	
			  		\begin{itemize}
	                   		\item[] Developed a comprehensive data collection and analysis tool to optimize Skydeck event attendance among startups.
	                   		\item[] Designed and created a financial analysis tool to measure and predict startup success using Skydeck's history of startup acquisitions, employee counts, and other various team metrics.
	                  \end{itemize}
                  	 
                  	 
                  Gradescope. Berkeley, CA.
                  \newline	 
                 		\hspace*{1em}\begin{tabu}{X[l]X[r]}
                  		Android Developer & September 2014 - July 2016
                 		\end{tabu}
                 			\hspace*{1em}
                 			\begin{itemize}					        
                   			\item[] Collaborated with team members to design and implement a comprehensive mobile API for better student user experience.
                   			\item[] Designed and built a comprehensive alpha mobile application for students to enhance the mobile homework submission user experience.
                  		 \end{itemize}
                  
\section*{PROJECTS}
				Muser - A Music Player for Reddit
                 \hspace*{1em}\begin{itemize}
                 		\item[] Designed and wrote an application to aggregate music from online music communities into categorical playlists using Kotlin, RxJava, Retrofit, and an MVP architecture to bulid presenters and views with minimal state and mutability.
                 \end{itemize}
                
				Computer Science Education at Berkeley High School
			
				\begin{itemize}
					\item[] Taught Freshman and Sophomore students at BHS basic programming skills and concepts using visual explanations and small coding projects. Additionally gave weekly mini-lectures on new computer science technologies and developments in the fields of machine learning, cybersecurity and distributed computing.	
				\end{itemize}

\section*{SKILLS}
				\setlength{\columnsep}{1pt}
				\begin{tabu}{X[2c]X[2c]X[c]X[c]}
					Android Development  & Project Management & Elixir& Kotlin \\
					Data Analysis 			   & Distributed Computing & Scala & Python \\
					Machine Learning		   & Functional Programming & Java & Elm \\
				\end{tabu}
 

\end{document}









