%! TEX program = xelatex
\documentclass[10pt]{article}
\usepackage[margin=0.75in]{geometry}

\usepackage{willres}
\usepackage{tabu}

\begin{document}

\titleheader{William Arnold}{(510){\textendash}529{\textendash}8523}{willarnold@berkeley.edu}
				 {linkedin.com/in/{\textasciitilde}arnold}      

\section*{EDUCATION}

\education{University of California, Berkeley, College of Engineering Class of 2021}
    {Bachelor of Science {\textendash} Electrical Engineering and Computer Science}
{GPA: 4.0, Dean's List}{Machine Learning}{Differential Geometry}


\section*{EXPERIENCE}

        \employer{Eluvio}{Berkeley, CA}{Cryptosystems Intern}{June 2020 --- August 2020}

                  \begin{accomplishments}
                \item Built a key{\textendash}splitting and distributed trust scheme to secure high value assets in a federated system.
                \item Designed and implemented a prototype consumer{\textendash}scale, identity{\textendash}based asset access scheme to allow content secured by an ethereum{\textendash}backed system to be securely and efficiently purchased. 
                  \end{accomplishments}

        \employer{Procore Technologies}{Santa Barbara, CA}
                {Machine Learning Intern}
                {June 2019 --- August 2019}
                    \begin{accomplishments}
                        \item Combined supervised image encoding with a Gaussian-based clustering algorithm in order to find latent classes in a dataset of construction images. 
                          This successfully produced a low-noise dataset 8x larger than any existing dataset and greatly increased model performance.
                        \item Built a web-based image annotation tool that increased manual data annotation efficiency by 220\%.
                    \end{accomplishments}

				\employer{Activate Inc., at Google}{San Francisco/Berkeley, CA}
								{Chief Technical Officer}
								{February 2016 --- August 2018}                  		
	                   \begin{accomplishments} 
	                    		\item Organized and implemented a feature{\textendash}diverse, spatial, unsupervised machine learning algorithm to identify the most attractive food concepts around 50+ locations in the Bay Area for a Fortune 500 company.
	                    		\item Collaborated with economists from NYU in order to create a scalable, demographic and restaurant quality{\textendash}based AI to predict restaurant success at 1000+ target locations across California.
                          \item Built a deep learning{\textendash}based model to predict how individuals move and eat in Google Cafes to reduce food waste and ensure more effective resource utilization in future Google buildings.
	                    \end{accomplishments}
	                    		
	   		
	   		\employer{Skydeck Berkeley}{Berkeley, CA}
	   			{Data Analyst and Ambassador}
	   			{July 2016 --- July 2018}
			  		\begin{accomplishments}
	                   		\item Developed a data analysis tool to measure Skydeck event attendance and effectiveness among startups.
	                   		\item Designed and created a financial analysis tool to measure and predict startup success using Skydeck's history of startup acquisitions, team backgrounds, employee counts, and other team metrics.
	                  \end{accomplishments}
                  	 
                  	 
                \employer{Gradescope}{Berkeley, CA}
                {Android Developer}{September 2014 --- July 2016}
                 			\begin{accomplishments}					        
                   			\item Designed and built a comprehensive beta Android app for students to enhance mobile the student homework submission experience.
                  		 \end{accomplishments}
                  		 
                  
\section*{ACTIVITIES}
        \project{CS70 Discreet Math and Probability Theory --- uGSI/TA }{August 2018 --- current}
        {Taught undergraduates taking discreet math and probability theory (CS70) at UC Berkeley, providing better insight into topics such as Galois Fields, Countabililty, and Probability Theory. Additionally, held office hours, proctored, and graded exams.}

\project{Cal Sailing Team --- Varsity Skipper and Fleetmaster}{August 2018 --- current}
        {Sailed and maintained FJs at Treasure Island Sailing Center and competed in Pacific Coast Conference Regattas. Was bowman for the Varsity boat in Big Sail 2018 against Stanford in J/22s at St Francis Yacht Club. Held racing tactics and sail trim lessons for team members.}


                
        %\project{Computer Science Education at Berkeley High School}
				%			{Taught Freshman and Sophomore students at BHS basic programming skills and concepts using visual explanations and small coding projects. Additionally gave weekly mini{\textendash}lectures on new computer science technologies and developments in the fields of machine learning, cybersecurity and distributed computing.}


\section*{SKILLS AND RELEVANT COURSES}
				\setlength{\columnsep}{.5pt}
				\begin{tabu}{X[2c]X[2.1c]X[2c]X[2c]}
					Quantum Computing    & Parallel Algorithms & Efficient Algorithms & Discrete Math \\
					Data Analysis 			   & Distributed Computing & Android Development & Honors Linear Algebra \\
          Machine Learning		   & Deep Learning & Probability Theory & Honors Analysis \\
				\end{tabu}
 
\end{document}









