%! TEX program = xelatex
\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}

\usepackage{sailingres}
\usepackage{tabu}

\begin{document}

\titleheader{William Arnold}{(510){\textendash}529{\textendash}8523}{willarnold@berkeley.edu}
				 {linkedin.com/in/{\textasciitilde}arnold}      

\section*{EDUCATION}

\education{University of California, Berkeley, College of Engineering Class of 2021}
    {Bachelor of Science {\textendash} Electrical Engineering and Computer Science}
{GPA: 4.0}{Machine Learning}{Computer Security}


\section*{EXPERIENCE}

        \boat{Santana 22 --- \it{Raven}}{Berkeley Yacht Club, CA}
								{Skipper, Trimmer, Tactician}
								{February 2013 --- current}                  		
                \begin{accomplishments}
                \item What I learned to sail on. 
                \item Logged 700+ hours aboard, at least 500 of which racing, and skippered ~25 races amounting to around 90 hours.
                \item Skippered in up to gale force 7 conditions, crewed in up to gale force 8. 
                 \end{accomplishments}
	                    		
        \boat{Officer --- Cal Sailing Team}{Treasure Island Sailing Center, CA}
        {Skipper, Crew}{August 2018 --- current}
              \begin{accomplishments}					        
              \item Competed in a J/22 slalom race as Bowman against Standford on the Cal Varsity boat in Big Sail 2018 at the St. Francis Yacht club.
                \item Competed in the Frosh-Soph college regatta on Mission Bay in San Diego as crew in FJs.
                \item Manage the team website.
               \end{accomplishments}
	   		
         \boat{Express 37 --- \it{Snowy Owl, Eclipse}}{Richmond Yacht Club, CA}
                {Main, Headsail, and Spin Trimmer, Bow}
                {July 2018 --- current}
                \begin{accomplishments}
                \item Competed in Express 37 Nationals at the Berkeley Yacht Club, mainly as headsail trim and spinnaker trim.
                \end{accomplishments}

\section*{Skills}
        \project{Advanced Prototyping and Fabrication}{August 2017 --- current}
                {Sailed FJs at Treasure Island Sailing Center and competed in Pacific Coast Conference Regattas. Was bowman for the Varsity boat in Big Sail 2018 against Stanford in J/22s at St Francis Yacht Club. Held racing tactics and sailing physics lessons for team members.}

        \project{CS70 Discreet Math and Probability Theory --- Tutor and Grader}{August 2018 --- current}
				{Tutored undegraduates taking discreet math and probability theory (CS70) at UC Berkeley, providing 	better insight into topics such as Galois Fields, Countabililty, and Computability. Additionally, graded homework.}

                
        %\project{Computer Science Education at Berkeley High School}
				%			{Taught Freshman and Sophomore students at BHS basic programming skills and concepts using visual explanations and small coding projects. Additionally gave weekly mini{\textendash}lectures on new computer science technologies and developments in the fields of machine learning, cybersecurity and distributed computing.}


\section*{SKILLS AND RELEVANT COURSES}
				\setlength{\columnsep}{.5pt}
				\begin{tabu}{X[2c]X[2.1c]X[2c]X[2c]}
					Android Development  & Project Management & Efficient Algorithms & Discreet Math \\
					Data Analysis 			   & Distributed Computing & Machine Structure & Honors Linear Algebra \\
					Machine Learning		   & Probability Theory & Systems and Controls & Circuit Design \\
				\end{tabu}
 
\end{document}









